Ants-Review: A Protocol For Open Anonymous Peer-Reviews\thanks{Supported by ETHTurin}

### 2020-06-04 paper-v1.tex
Updates from Overleaf

\section{Supplementary material}
Our open source code is available at the Github repository. A demo of the project is available at Youtube channel.
\section{CRediT Authorship Contribution Statement}
Bianca Trovò: Conceptualization, Investigation, Visualization, Writing - original draft, Writing - review & editing. Nazzareno Massari: Project administration, Methodology, Validation, Software development. Both authors equally contributed and supervised the project.
\section{Declaration of Competing Interest}
The authors declare no competing interests.

>>>>

\section{Supplementary material}
Our open source code is available at the Github repository. A demo of the project is available at Youtube channel.
\section{CRediT Authorship Contribution Statement}
Bianca Trovò: Conceptualization, Investigation, Visualization, Writing - original draft, Writing - review \& editing. Nazzareno Massari: Project administration, Methodology, Validation, Software development. Both authors equally contributed and supervised the project.
\section{Declaration of Competing Interest}
The authors declare no competing interests.
